\documentclass[11pt]{article}

\usepackage[
top=0.5in,
bottom=0.5in,
left=0.5in,
right=0.5in
]{geometry}

\usepackage{XCharter}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}

\raggedright
\pagestyle{empty}

\input{glyphtounicode}
\pdfgentounicode=1

\titleformat{\section}
{\bfseries\large}
{}
{0pt}
{}
[\vspace{1pt}\titlerule\vspace{-6pt}]

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-3pt,leftmargin=12pt,topsep=3pt}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\centerline{\Huge [Name] [Last Name]}

\vspace{4pt}

\centerline{
\href{mailto:email@example.com}{email@example.com}
\;|\;
City, Country
\;|\;
\href{https://linkedin.com/in/your-linkedin}{linkedin.com/in/your-linkedin}
\;|\;
\href{https://github.com/your-github}{github.com/your-github}
}

\vspace{-10pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Profile}

Full-stack software engineer specializing in AI-powered data platforms and backend systems. Experienced building scalable data ingestion pipelines, cloud-native services, and production AI workflows on Google Cloud using Python, React, Django, FastAPI, and Vertex AI. Comfortable owning features end-to-end while collaborating closely with ML engineers and domain experts. Native Italian, fluent English (C1), working Dutch (A2).

\vspace{-8pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Experience}

\textbf{Full-Stack Developer} AI-driven procurement \& spend-intelligence
\hfill
Mar 2023 -- Sep 2024

\vspace{-8pt}

\begin{itemize}
    \item Built production full-stack features using Django, Celery, React, TypeScript and Material UI on Google Cloud.
    \item Designed and implemented a self-service data ingestion platform, replacing manual onboarding and maintenance with event-driven workflows.
    \item Automated the Purchase Price Variance (PPV) lifecycle—from detection to resolution—reducing average resolution time from \textbf{48 hours to approximately 2 hours (95\% improvement)} through real-time streaming, ML-based classification, and automated workflows.
    \item Developed data ingestion services (\textit{cat-ingestion}, \textit{cat-data}, \textit{cat-material}) powering procurement KPIs for enterprise customers.
    \item Integrated Vertex AI models including zero-shot classification, BERT similarity grouping, and GPT-assisted product tagging.
    \item Partnered with ML engineers to integrate production AI models and collaborated with procurement domain experts to translate complex business processes into scalable software.
    \item Designed technical architecture for major platform initiatives, secured CTO approval, and coordinated implementation across engineering stakeholders.
\end{itemize}

\textbf{Full-Stack Developer Intern} AI-powered marketing intelligence platform
\hfill
Aug 2022 -- Jan 2023

\vspace{-8pt}

\begin{itemize}
    \item Built a FastAPI configuration service serving as the single source of truth for account and pipeline configuration.
    \item Containerized services with Docker and maintained Jenkins CI pipelines.
    \item Improved deployment consistency by centralizing configuration management across internal services.
\end{itemize}

\textbf{Career Break}
\hfill
Oct 2024 -- Jul 2026

\vspace{2pt}

Planned career break for family and health reasons while continuing to develop software engineering skills through personal projects. Fully recovered and available for full-time software engineering roles.

\vspace{-8pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Skills}

\textbf{Languages:} Python, TypeScript, SQL (PostgreSQL, MySQL, BigQuery), Go, Java

\textbf{Frontend:} React, Material UI, Tailwind CSS, D3.js, Apache ECharts, Firebase, Auth0

\textbf{Backend:} Django, FastAPI, Celery, SQLAlchemy, REST APIs

\textbf{Data \& AI:} Data Ingestion, ETL Pipelines, Vertex AI, HuggingFace Transformers, BERT, GPT, Streamlit

\textbf{Cloud:} Google Cloud Platform (Cloud Run, BigQuery, Pub/Sub), Terraform, Docker, Jenkins

\textbf{Tools:} Git, Figma, pytest, Cypress, AI coding agents

\vspace{-8pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Languages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Languages}

Italian (Native) \hfill English (C1) \hfill Dutch (A2)

\vspace{-8pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Education}

\textbf{B.Sc. Computer Science} (in progress)\\
University of Milan

\vspace{-8pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Interests
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Interests}

Artificial Intelligence, Data Engineering, Finance, Formula 1, Photography, Cooking.



\end{document}