\documentclass[11pt]{article}

\usepackage[
top=0.5in,
bottom=0.5in,
left=0.5in,
right=0.5in
]{geometry}

\usepackage{XCharter}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}

\raggedright
\pagestyle{empty}

\input{glyphtounicode}
\pdfgentounicode=1

\titleformat{\section}
{\bfseries\large}
{}
{0pt}
{}
[\vspace{1pt}\titlerule\vspace{-6pt}]

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-3pt,leftmargin=12pt,topsep=3pt}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\centerline{\Huge [Name] [Last Name]}

\vspace{4pt}

\centerline{
\href{mailto:email@example.com}{email@example.com}
\;|\;
City, Country
\;|\;
\href{https://github.com/your-github}{github.com/your-github}
}
\vspace{4pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Summary
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Full-stack software engineer specializing in AI-powered data platforms and scalable backend pipelines. Experienced in owning features end-to-end, integrating production AI models, and building cloud-native services on Google Cloud using Python, Django, and React. Returning to the workforce after a planned career break, fully recovered and actively developing skills through personal projects.

\vspace{-8pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Education}
%\textbf{Company Location} -- B.Sc. Computer Science \hfill Expected 2026
\textbf{[University Name]} -- B.Sc. Computer Science \hfill Expected 2026

\textit{Relevant coursework:} Machine Learning, Databases, Cloud Computing, Algorithms \& Data Structures

\vspace{-8pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Experience}

\textbf{Software Engineer} | AI-driven procurement \& spend-intelligence platform
\hfill
Mar 2023 -- Sep 2024

\textit{Tech:} Django, FastAPI, React, TypeScript, PostgreSQL, BigQuery, Vertex AI, Pub/Sub, Cloud Run

\vspace{-8pt}

\begin{itemize}
    \item Led design and delivery of a data ingestion platform that automated customer onboarding, cutting setup from \textbf{3 days to <1 hour (99\% reduction)} and enabling zero-touch onboarding for <10 enterprise clients.
    \item Architected and shipped a real-time Purchase Price Variance (PPV) detection system using Pub/Sub streaming, BigQuery analytics, and ML classification, cutting identification time from \textbf{1--4 weeks to 2 hours}.
    \item Built and maintained production ML pipelines on Vertex AI for transaction classification and grouping using zero-shot (sentence-transformers), FAISS similarity search, and GPT-assisted product matching workflows.
    \item Developed core data ingestion services supporting \textbf{billions of rows} of procurement data from heterogeneous sources (Excel, CSV, APIs), implementing robust parsing and validation for enterprise procurement data.
    \item Owned end-to-end feature development across the stack: designed technical architecture, secured CTO approval, coordinated cross-team implementation, and shipped 15+ production features.
    \item Improved data pipeline reliability by implementing comprehensive observability (logging, monitoring, alerting) and automated testing (pytest, Cypress) for critical ingestion workflows.
\end{itemize}

\textbf{Software Engineer Intern} | AI-powered marketing intelligence platform
\hfill
Aug 2022 -- Jan 2023

\textit{Tech:} FastAPI, Python, Docker, Jenkins, Terraform, MySQL

\vspace{-8pt}

\begin{itemize}
    \item Designed and built a FastAPI configuration management service as the single source of truth for pipeline and account settings, reducing configuration drift across 10+ internal services.
    \item Containerized microservices with Docker and maintained Jenkins CI/CD pipelines, cutting deployment time from 30 minutes to 5 minutes through automation and standardized build steps.
    \item Collaborated with senior engineers to refactor legacy data pipelines, improving maintainability and cutting incident response time by 40\% through automated monitoring.
    \item Implemented infrastructure-as-code (Terraform) for consistent provisioning across dev, staging, and production environments, eliminating manual setup.
\end{itemize}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Skills}

\textbf{Languages:} Python, TypeScript, SQL (PostgreSQL, MySQL, BigQuery), Go, Java

\textbf{Frontend:} React, Material UI, Tailwind CSS, D3.js, Apache ECharts, Firebase, Auth0

\textbf{Backend:} Django, FastAPI, Celery, SQLAlchemy, REST APIs

\textbf{Data \& AI:} Data Ingestion, ETL Pipelines, Vertex AI, HuggingFace Transformers, BERT, GPT, Streamlit

\textbf{Cloud:} Google Cloud Platform (Cloud Run, BigQuery, Pub/Sub), Terraform, Docker, Jenkins

\textbf{Tools:} Git, Figma, pytest, Cypress, AI coding agents

\vspace{-8pt}

\end{document}